% Setting up the document class for presentation
\documentclass[11pt]{beamer}

% Including essential packages
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{xcolor}
\usepackage{hyperref}

% Defining theme and colors
\usetheme{metropolis}
\definecolor{primary}{RGB}{0, 102, 204}
\definecolor{secondary}{RGB}{255, 153, 51}
\setbeamercolor{frametitle}{bg=primary, fg=white}
\setbeamercolor{normal text}{fg=black}
\setbeamerfont{title}{size=\large}
\setbeamerfont{frametitle}{size=\normalsize}

% Configuring fonts (using a clean sans-serif font)
\usepackage[sfdefault]{lmodern} % Fallback sans-serif font

% Title slide information
\title{AI Trainer: Pose Recognition Web App}
\subtitle{Revolutionary Real-Time Pose Detection for Fitness and Training}
\author{xAI}
\date{July 09, 2025, 11:22 AM IDT}

\begin{document}

% Creating title slide
\begin{frame}
    \titlepage
\end{frame}

% Introducing AI Trainer
\begin{frame}{Introducing AI Trainer}
    \begin{itemize}
        \item Real-time pose recognition
        \item Offline functionality
        \item Customizable pose settings
        \item User-friendly interface
    \end{itemize}
\end{frame}

% Core Features
\begin{frame}{Core Features}
    \begin{block}{Pose Recognition System}
        \begin{itemize}
            \item Real-time webcam-based detection
            \item Supports 1-7 customizable poses
            \item Visual comparison with reference images
            \item Confidence scoring system
        \end{itemize}
    \end{block}
    \begin{block}{Customization Options}
        \begin{itemize}
            \item Adjustable accuracy (up to 100%)
            \item Configurable recognition delay (0-3 seconds)
            \item Editable pose names
            \item Audio feedback toggle
        \end{itemize}
    \end{block}
\end{frame}

% GUI: Pose Settings Interface
\begin{frame}{GUI: Pose Settings Interface}
    \small{This interface provides all buttons with clear function explanations. Key features include:
    - "Refresh (Restart from Pose 1)": Resets the pose sequence.
    - "Back to Settings": Returns to configuration options.
    - Confidence slider: Adjusts the detection threshold up to 100%.
    - Pose Settings: Displays the current and expected poses.
    - Distance feedback: Guides user positioning.}
\end{frame}

% GUI: Pose Detection Interface
\begin{frame}{GUI: Pose Detection Interface}
    \small{This interface displays the recognition screen with real-time pose detection. Features include:
    - Skeletal tracking with keypoint overlays.
    - Current pose display and expected pose indication.
    - Visual feedback with a reference image.
    - Distance and positioning guidance.}
\end{frame}

% Easy Setup Process
\begin{frame}{Easy Setup Process}
    \begin{enumerate}
        \item Train a model using Teachable Machine
        \item Upload model files (model.json, metadata.json, weights.bin)
        \item Configure poses and settings
        \item Start recognition with a webcam
    \end{enumerate}
    \vspace{0.5cm}
    \begin{alertblock}{No Internet Required}
        Fully offline after initial setup
    \end{alertblock}
\end{frame}

% Get Started Today!
\begin{frame}{Get Started Today!}
    \begin{center}
        \Large Transform your training experience with AI Trainer\\
        \vspace{0.5cm}
        \href{https://x.ai/grok}{\color{primary}Learn More at x.ai}
    \end{center}
    \begin{block}{Contact Us}
        For API integration or custom solutions, visit \href{https://x.ai/api}{\color{primary}x.ai/api}
    \end{block}
\end{frame}

\end{document}